\proglang{collapse}: Advanced and Fast Statistical Computing and Data Transformation in \proglang{R}

### 2024-03-20 misc/JSS article/jss-article-rnw/article.Rnw
Using memory efficiency.

%% - \Abstract{} almost as usual
\Abstract{
\pkg{collapse} is a large \proglang{C/C++}-based infrastructure package facilitating complex statistical computing, data transformation, and exploration tasks in \proglang{R} - at outstanding levels of performance and programming efficiency. It also implements a class-agnostic approach to \proglang{R} programming, supporting vector, matrix and data frame-like objects and their popular variants (e.g., \class{factor}, \class{ts}, \class{xts}, \class{tibble}, \class{data.table}, \class{sf}), enabling its seamless integration with large parts of the \proglang{R} ecosystem. This article introduces the package's key components and design principles in a structured way, supported by a rich set of examples. A small benchmark demonstrates its computational performance.
%  This short article illustrates how to write a manuscript for the
%  \emph{Journal of Statistical Software} (JSS) using its {\LaTeX} style files.
%  Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
%  it is recommended to keep the {\LaTeX} code as simple as possible,
%  i.e., avoid inclusion of packages/commands that are not necessary.
%  For outlining the typical structure of a JSS article some brief text snippets
%  are employed that have been inspired by \cite{Zeileis+Kleiber+Jackman:2008},
%  discussing count data regression in \proglang{R}. Editorial comments and
%  instructions are marked by vertical bars.
}

>>>>

%% - \Abstract{} almost as usual
\Abstract{
\pkg{collapse} is a large \proglang{C/C++}-based infrastructure package facilitating complex statistical computing, data transformation, and exploration tasks in \proglang{R} - at outstanding levels of performance and memory efficiency. It also implements a class-agnostic approach to \proglang{R} programming, supporting vector, matrix and data frame-like objects and their popular variants (e.g., \class{factor}, \class{ts}, \class{xts}, \class{tibble}, \class{data.table}, \class{sf}), enabling its seamless integration with large parts of the \proglang{R} ecosystem. This article introduces the package's key components and design principles in a structured way, supported by a rich set of examples. A small benchmark demonstrates its computational performance.
%  This short article illustrates how to write a manuscript for the
%  \emph{Journal of Statistical Software} (JSS) using its {\LaTeX} style files.
%  Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
%  it is recommended to keep the {\LaTeX} code as simple as possible,
%  i.e., avoid inclusion of packages/commands that are not necessary.
%  For outlining the typical structure of a JSS article some brief text snippets
%  are employed that have been inspired by \cite{Zeileis+Kleiber+Jackman:2008},
%  discussing count data regression in \proglang{R}. Editorial comments and
%  instructions are marked by vertical bars.
}
